Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-08 paper/paper.tex
explaining fuzzers

\Mar{revise...}~We used representatives of popular fuzzing approaches. For
random-based fuzzing we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).
Our infrastructure supports any grammar fuzzer with a few adjusts. However, 
we try to integrate several grammar-based fuzzers, for example 
Grammarinator~\footnote{https://github.com/renatahodovan/grammarinator}, QuickFuzz~\cite{grieco2016quickfuzz}
and \Fix{others fuzzers} to generate new JavaScript files based on grammar, but 
after several runs it was observed that this approach was ineffective
due the amount of invalid files and/or files without discrepancies. For example, if we ran 
Grammarinator to generate 1K JS files ten times with a random seed generation, we obtained
\Fix{XX\%} of valid files. Checking in our environment almost \Fix{XX\%}
are js files that shows undefined variables and due the differential testing in our environment
all engines will raise a SyntaxError and this approach was not relevant to our experiment.

>>>>

In the following, we describe the list of fuzzers we analyzed. We
initially considered generational grammar-based fuzzers and mutational
fuzzers.

Grammar-based fuzzers generate a new file using the grammar of the
language whose inputs should be fuzzed. Intuitively, those fuzzers
implement a traversal of the production rules of the input grammar to
create syntax trees, which are then pretty-printed. Consequently, this
approach produces inputs that are syntatically valid by construction.
We analyzed two grammar-based
fuzzers--Grammarinator~\cite{grammarinator} and
QuickFuzz~\cite{grieco2016quickfuzz}.  Unfortunately none was
effective out of the box. Given the bound limits we defined, we were
unable to find any discrepancy in the inputs those tools generated. To
sum, the tools produced a high percentage of semantically-invalid
inputs such as \Fix{give one or two concrete examples--variable usage
  without definition?} that we needed to discard and the valid inputs
manifested no discrepancies. For example, we produced 10K inputs with
Grammarinator and only \Fix{X} were valid. With QuickFuzz, we were
able to produce \Fix{Y, Y$>$Y?} valid inputs as it contains some
heuristics to avoid generation of semantically-invalid
inputs. Nonetheless, running those inputs in our infrastructure we
were unable to find discrepancies. Inpecting the valid inputs we found
that they produced only very simple inputs. \Mar{are there weights
  associated with production rules besides the depth you can set?}

%% Our
%% infrastructure supports any grammar fuzzer with a few
%% adjusts. However, we try to integrate several grammar-based fuzzers,
%% for example
%% and \Fix{others fuzzers} to
%% generate new JavaScript files based on grammar, but after several runs
%% it was observed that this approach was ineffective due the amount of
%% invalid files and/or files without discrepancies.
%% For example, if we
%% ran Grammarinator to generate 1K JS files ten times with a random seed
%% generation, we obtained \Fix{XX\%} of valid files. Checking in our
%% environment almost \Fix{XX\%} are js files that shows undefined
%% variables and due the differential testing in our environment all
%% engines will raise a SyntaxError and this approach was not relevant to
%% our experiment.

%% We initially considered used representatives of popular fuzzing approaches. For
%% random-based fuzzing we used Radamsa~\cite{radamsa}; for
%% coverage-based fuzzing we used
%% \Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
%% generative-based fuzzing we used
%% \Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
%% be found elsewhere~\cite{fuzz-bart}.

\Fix{do the same as above for coverage-based fuzzing}

\Fix{do the same as above for black-box fuzzing}
